---
output:
  pdf_document: default
  html_document: default
---

---
title: \textbf{Homework 1}
author: "Juwon Lee, Economics and Statistics, UCLA"
date: "2023-01-13"
output: 
  pdf_document:
    latex_engine: xelatex
---

tinytex::install_tinytex()

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1. Review on simple linear regression.

\noindent (1) B. They have moderate negative linear relationship.

\noindent (2) 
$$\text{Correlation Coefficient}~r = \sqrt{R^2} = \sqrt{0.4117} \approx 0.64164$$

\noindent (3) This is
$$ \hat{\beta_1} = r * \frac{s_Y}{s_X} = 0.64164 * \frac{5}{10.84} \approx 0.29596$$
$$ \hat{\beta_0} = \bar{Y} - \hat{\beta_1} * \bar{X}  = 20.16 - \hat{\beta_1} * 20.97 \approx 13.95375$$

\noindent It means that we can make a 'model' to estimate 
$Y$ such that $Y = \hat{\beta_0} + \hat{\beta_1} X$.

\noindent (4) C. About 41\% of the total variability in strength of deltoid muscle is explained by the model.

\noindent (5) C. It does not have any apparent pattern and it implies the good fit of the model.

\noindent (6) It means that $X=35$, so that
$$ Y = \hat{\beta_0} + \hat{\beta_1} X \approx 13.95375 + 0.29596 * 35 = 24.31230 $$

## 2. Review on Hypothesis testing.

\noindent (1) $H_0 : \mu=5.7~~\text{vs}~~H_1: ~ \mu < 5.7$.

\noindent (2) Because $n=36 > 30$, we can use $z$-statistic,
$$ z = \frac{5.1 - 5.7}{1.4 / \sqrt{36}} \approx -2.57143$$
\noindent (3) $P(z \leq -2.57143) \approx 0.00506$.

```{r}
pnorm((5.1 - 5.7) / (1.4 / (36)^(1/2)))
```

\noindent (4) $p$-value $\approx$ 0.00506 < 0.05, so we can ignore the null.  
Thus, we can't say that the number of introverts are 5.7.

\noindent (5) $(5.7 - z_{0.025} * \frac{1.4}{\sqrt{36}},~5.7 + z_{0.025} * \frac{1.4}{\sqrt{36}}) \approx (5.24268,~6.15733)$.

\noindent (6) Thus, if the sample mean is included in this interval, then we can say that the null hypothesis can be rejected.
\noindent Thus, because $\bar{X} = 5.1$, we can reject the null.

\newpage

## 3. Review on R programming

First of all, we can make a dataset by the csv file.

```{r}
heart <- read.csv("/Users/user/Desktop/Yonsei/Junior/3-2/Introduction to Data Analysis and Regression/Heart.csv")

heart1 <- heart[c(6,9)]
head(heart1)
```

\noindent (1) 

```{r}
MaxHR <- as.vector(heart1[2])
Chol <- as.vector(heart1[1])

data_lm <- lm(MaxHR~Chol, data=heart1)
data_lm
```

\newpage
```{r lmtest}
summary(data_lm)
```

\noindent Thus, $y = 149.981292 -0.001516x$.

\noindent (2)

```{r ggplot2, r heart1}
plot(heart1)
abline(149.981292, -0.001516, col='red')
```

\newpage
\noindent (3) The R-squared in summary is 1.178e-05.  
We have to use standardized residuals, so that

```{r ggplot2}
sres <- data_lm$residuals/sqrt(var(data_lm$residuals))
plot(sres)
```

\noindent If the residual plots does not show any pattern, then the model is supposed to be a good fit. However, in this case, the residual plot is almost the same as the scatter plot, suggesting that the model provides little information. Therefore, it is a poor fit.

## 4. Pre-Course Survey

\noindent I have completed the Pre-Course Survey. Thank you.